### 2017-10-13 Draft2.tex
Finish the skeleton of "Adding"
Add more skeletons
Add primes to the resize list fns
More variables
Add description of big-P notation

\newcommand{\tcomplex}{\textbf{Time complexity}}
\newcommand{\scomplex}{\textbf{Space complexity}}

@@

@@

@@

	\begin{align*}
	\nwritesfn(\varnitems) = \biggo(\varnitems)
	\end{align*}

@@

	\begin{align*}
	\spacefn(\varnitems) = \biggo(2^{\lceil \log_2 \varnitems \rceil}) = \bigo(\varnitems)
	\end{align*}

@@

@@

>>>>

\newcommand{\tcomplex}{\textbf{Time complexity}}
\newcommand{\scomplex}{\textbf{Space complexity}}
\newcommand{\tcomplexcmp}{\textbf{Time complexity comparison}}
\newcommand{\scomplexcmp}{\textbf{Space complexity comparison}}

@@

\newcommand{\timenewfn}{\timefn'}
\newcommand{\spacenewfn}{\spacefn'}
\newcommand{\nwritesnewfn}{\nwritesfn'}

\newcommand{\timeratio}{r_\timefn}
\newcommand{\spaceratio}{r_\spacefn}

@@

	The following mathematical definitions will be used while analyzing time and space complexity:

	\begin{description}
		\item[$\biggo(f(n))$] This is an alternative to big-O notation for time complexity; I will call it \textbf{big-P notation}.
			\subitem The main purpose of big-P notation is to preserve the constant coefficient of the fastest-growing term in $f(n)$, while still maintaining many properties of big-O. For example, $\bigo(2n) = \bigo(n)$, but $\biggo(2n) \neq \biggo(n)$. This makes it possible to compare time complexities whose ratio converges to a constant as $n$ becomes larger.
			\subitem More formally, $\biggo(f(n)) = \biggo(g(n))$ iff $$\lim_{n \to \infty} {\frac{f(n)}{g(n)}} = 1$$.
	\end{description}

@@

	\begin{align*}
	\nwritesnewfn(\varnitems) = \biggo(\varnitems)
	\end{align*}

@@

	\begin{align*}
	\spacenewfn(\varnitems) = \biggo(2^{\lceil \log_2 \varnitems \rceil}) = \bigo(\varnitems)
	\end{align*}

	\tcomplexcmp

	\begin{align*}
	\end{align*}

	\scomplexcmp

	\begin{align*}
	\spaceratio = \frac {\biggo(2^{\lceil \log_2 \varnitems \rceil})} {\biggo(2^{\lceil \log_2 \varnitems \rceil + 1})} = \frac{1}{2}
	\end{align*}

@@

	$\timefn(\varnitems) = \bigo(1)$

	$\timenewfn(\varnitems) = \bigo(1)$

	\tcomplexcmp

@@

	$\timefn(\varnitems) = \bigo(\varnitems)$

	$\timenewfn(\varnitems) = \bigo(\varnitems)$

	\tcomplexcmp
